### 2018-07-24 pilot_manuscript.Rmd
Added new models

```{r load_packages, include = FALSE}
library("papaja") #R says this package doesn't exist in current version :/
library(MuMIn)
knitr::opts_chunk$set(cache = TRUE)
```
# Introduction
Talk about MFT, MFQ, MFD (primer on moral psychology?)

@@

>>>>

```{r load_packages, include = FALSE}
library(papaja) #R says this package doesn't exist in current version :/
library(MuMIn)
knitr::opts_chunk$set(cache = TRUE)
```
# Introduction
Talk about MFT, MFQ, MFD (primer on moral psychology?)

@@

####NEW MODELS####

##overall percent - no random intercept
model4 = lme(percent ~ 1,
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|partno) #How to get rid of intercept??
summary(model4)
r.squaredGLMM(model4)

##overall percent - random intercept by source
model4.1 = lme(percent ~ 1,
             data = long_mlm, 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model4.1)
r.squaredGLMM(model4.1)

##MFD category ~ lean 
model5.1 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "hperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.1)
r.squaredGLMM(model5.1)

model5.2 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "hperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.2)
r.squaredGLMM(model5.2)

model5.3 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "fperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.3)
r.squaredGLMM(model5.3)

model5.4 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "fperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.4)
r.squaredGLMM(model5.4)

model5.5 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "iperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.5)
r.squaredGLMM(model5.5)

model5.6 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "iperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.6)
r.squaredGLMM(model5.6)

model5.7 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "aperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.7)
r.squaredGLMM(model5.7)

model5.8 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "aperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.8)
r.squaredGLMM(model5.8)

model5.9 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "pperhi", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.9)
r.squaredGLMM(model5.9)

model5.10 = lme(percent ~ lean,
             data = long_mlm[long_mlm$moraltype == "pperlo", ], 
             method = "ML", 
             na.action = "na.omit",
             random = ~1|Source)
summary(model5.10)
r.squaredGLMM(model5.10)
